Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-26 Web3D2013-Dec3D/paper.tex
Changed 'DFKI GmbH' to just 'DFKI' and 'Universität des Saarlandes' to 'Saarland University'

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ Inria \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI GmbH \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI GmbH \& Universit\"at des Saarlandes \\ Saarbr\"ucken \\ Germany
}

>>>>

\author{
Jacek Jankowski\thanks{e-mail:jacek.jankowski@inria.fr} \\ Inria \\ Bordeaux \\ France
\and Sandy Ressler\thanks{e-mail:sandynist@gmail.com} \\ NIST \\ Gaithersburg MD \\ USA
\and Kristian Sons\thanks{e-mail:kristian.sons@dfki.de} \\ DFKI \\ Saarbr\"ucken \\ Germany
\and Yvonne Jung\thanks{e-mail:yvonne.jung@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Johannes Behr\thanks{e-mail:johannes.behr@igd.fraunhofer.de} \\ Fraunhofer IGD \\ Darmstadt \\ Germany
\and Philipp Slusallek\thanks{e-mail:slusallek@cs.uni-saarland.de} \\ DFKI \& Saarland University \\ Saarbr\"ucken \\ Germany
}
